---
title: "Simulate static temperature"
author: "Jun Su"
date: "2023-04-29"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/sujun/Documents/GitHub/Bacillus-cereus-exposure-assessment-model")
```

# set environment
```{r}
# load packages 
library(tibble)
library(dplyr)
library(tidyr)
library(formula.tools)    # to load 'rhs'
library(purrr)            # to load 'map'
library(deSolve)          # to load 'ode'
library(rlang)

# load utility functions
source("Exposure assessment model/UtilityFunctions_dynamic_growth.R")
```

# generate simulation input
```{r}
data_Q0 = read.csv("Exposure assessment model/InputFiles/Q0_h0_summary.csv")
data_Nmax = read.csv("Exposure assessment model/InputFiles/Nmax_new.csv")
data_sec_model = read.csv("Exposure assessment model/InputFiles/sec_model_new.csv")
Clade = c("I","II","VII","IV","IV","IV","IV","II","III","IV","II","VII","II","V","V","IV")
simulation_input <- data.frame(isolate = data_Q0$isolate, 
                               Q0 = data_Q0$Q0, 
                               Nmax = data_Nmax$average_Nmax, 
                               b = data_sec_model$Slope, 
                               Tmin = data_sec_model$Tmin,
                               Clade)
simulation_input$Topt = sapply(simulation_input$Clade, xopt_func)
simulation_input$mu_opt = (simulation_input$b*(simulation_input$Topt-simulation_input$Tmin))^2 
```

# predict B cereus growth at static temperature < Tmin over 90 days
```{r}
# create a tibble with environmental conditions over time (3dC)
env_cond_time <- c(0:90)
env_cond_temp <- 3

# group the data by isolate name
simulation_input_groups <- simulation_input %>% 
  group_by(isolate)

# run simulation (3dC)
count_d90_by_isolate <- simulation_input_groups %>%
  nest() %>%
  mutate(
    count_d90 = map(data, ~{
      my_primary <- list(mu_opt = .$mu_opt, Nmax = .$Nmax, N0 = 1e2, Q0 = .$Q0)
      sec_temperature <- list(model = "reducedRatkowsky", xmin = .$Tmin, b = .$b, clade = .$Clade)
      my_secondary <- list(temperature = sec_temperature)
      growth <- predict_dynamic_growth(
        times = env_cond_time,
        env_conditions = tibble(time = env_cond_time, temperature = rep(env_cond_temp, 91)),
        my_primary,
        my_secondary
      )
      sim <- growth$simulation
      tail(sim$logN, 1)
    })
  ) %>%
  select(isolate, count_d90)

count_d90_by_isolate <- as.data.frame(count_d90_by_isolate)
simulation_Tmin_result = do.call(rbind,count_d90_by_isolate)
write.csv(simulation_Tmin_result,"Exposure assessment model/OutputFiles/sanity_check_result.csv")
```



